\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}

\textbf{\huge  Math 340A - Summer 2018}
\begin{itemize}
    \item
        Instructor: Kevin Lui
    \item
        Email: \href{mailto:klui@uw.edu}{klui@uw.edu}
    \item
        Webpage: \url{kevinlui.org/su18m340a}
    \item
        Office: Padelford C-8D
\end{itemize}

\textbf{Office Hours}

See the course page for office hours.

\textbf{Outline}

The textbook is Linear Algebra, 4th Edition, Friedberg, Insel and Spence. I
will reference this book and assign some problems from it.  

Topics include vector spaces, bases, linear transformations, matrix operations,
determinants, eigen-stuff, inner products.  This course is intended to be a
second exposure to linear algebra. There will be an emphasis on proofs and
rigor. But we will also cover applications and computations (with a computer).

\textbf{Grading}

Based on total class percentages, I will choose decide which percentages
correspond to a 4.0, the class median, 2.0, and 0.7. The rest of the grades
will decided using a piecewise-linear function.

\begin{tabular}{ l r }
    Category  & Weight   \\
    \hline
    Homework  & 20\%      \\
    Quizes  & 20\%      \\
    Midterm (Week 5 - 7/20) & 25\%      \\
    Final (Last day - 8/17)    & 35\%
\end{tabular}

\textbf{Homework}

There will be weekly homework posted each Monday due the following Monday.
There is a grader for this course.  The grader is allowed to reject any
assignment if it is incomprehensible or illegible.  Not all problems will be
looked at. A few problems will are graded for correctness. A few problems will
 be graded for completion.  The lowest homework score will be dropped.

\textbf{Quizzes}

There is a short 15-minute quiz each Friday. The lowest quiz score is dropped.

\textbf{Makeup Exams}

In the case of religious holidays or participation in certain university
sponsored events, arrangements must be made as soon as possible. Otherwise, I
will give you a makeup quiz or exam only in unavoidable, compelling, and
well-documented circumstances. If you are extremely sick, you must bring me a
doctor's note that states you were incapable of taking the quiz or exam. 

Do not miss the exams for travel reasons. You are expected to be here for the
midterm and final.

\end{document}
