\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}

\textbf{\huge  Math 308L - Autumn 2017 }
\begin{itemize}
    \item
        Instructor: Kevin Lui
    \item
        Email: \href{mailto:klui@uw.edu}{klui@uw.edu}
    \item
        Webpage: \url{kevinlui.org}
    \item
        Office: Padelford C-8D
\end{itemize}

\textbf{Office Hours}
Office hours will be held in Padelford C-8D. The time will be decided the first
week of class.

\textbf{WebAssign/Book}

We will use \textit{Linear Algebra with Applications, Second Edition} by
Jeffrey Holt. You must have a WebAssign code to complete the homework. This
code gives access to a electronic version of the book. Dr. Andrew Loveless
wrote some really detailed instructions on WebAssign here:
\url{https://sites.math.washington.edu/~m124/WebassignInstructions.pdf}

\textbf{Objectives}

The goal of this course is to introduce students to matrix algebra. Topics
include linear systems of equations, linear independence and span, linear
transformations, inverses, vector spaces, determinants, eigenvalues and
eigenvectors, and the Gram-Schmidt process.

\textbf{Grading}

The class is curved in such a way that the median score will be around a 3.0. I
will provide a grade estimate after each midterm.  The grades will be weighed
as follows:

\begin{tabular}{ l r }
    Category  & Weight   \\
    \hline
    Homework  & 20\%      \\
    Midterm 1 (Week 4 - 10/18) & 20\%      \\
    Midterm 2 (Week 8 - 11/15) & 20\%      \\
    Final (12/14)    & 40\%
\end{tabular}

\textbf{Homework}

Homework assignments are done through WebAssign. The due dates for each
assignment will be posted there. You are expected to complete each assignment 2
days before the official due date. I will not grant homework extensions.

I will add 10\% to your homework grade unless you are already above a 90\%.

Occasionally, I will occasionally post some additional problems for you to look
at. They are optional. I will not collect or grade them. The goal of these
problems will be to strengthen your conceptual and geometric understanding of
the material. Exam problems will be inspired by these additional problems.

\textbf{Exams}

You are allowed the Ti-30x IIS calculator and a single sheet of 2-sided
handwritten self written notes.

\textbf{Makeup Exams}

There will be no makeup exams.

In the case of religious holidays or participation in certain university
sponsored events, arrangements must be made as soon as possible. Otherwise, I
will excuse you from an exam only in unavoidable, compelling, and
well-documented circumstances. If you are extremely sick, you must bring me a
doctor's note that states you were incapable of taking the quiz or exam. If you
are excused from a midterm, your other midterm and final will be weighed more
heavily.

If you are not excused and you miss an exam, you will receive a zero.

\end{document}
