\documentclass{exam}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}

\begin{center}
    Worksheet 8 - Never due
\end{center}

\begin{questions}
    \question
    Give an example of each of the following. If it is not possible, write
    ``NOT POSSIBLE''.
    \begin{parts}
        \part
        Give an example of a basis of $\mathbb{R}^4$ such that each element
        lies in the hyperplane $2w+3x+y+z=0$.
        \part
        Give an example of a basis of $\mathbb{R}^4$ such that each element
        lies in the hyperplane $2w+3x+y+z=1$.
        \part
        Give an example of a matrix that is orthogonally diagonalizable but not
        diagonalizable.
        \part
        Give an example of a matrix that is diagonalizable but not orthogonally
        diagonalizable.
        \part
        Give an example of a nonzero matrix $A$ such that $A^2=0$.
        \part
        Give an example of a nonzero matrix $A$ such that $A^2=I$.
        \part
        Give an example of a nonzero matrix $A$ such that $A^2=I$ and the
        nullity of $A$ is 1.
        \part
        Give an example of an orthogonal set that is not linearly independent.
        \part
        Give an example of an orthogonal set that is not spanning.
        \part
        Give an example of a $2\times 3$ matrix whose rank is equal to its
        nullity.
        \part
        Give an example of 2 matrices $A$ and $B$ such that $A^3=B^3$.
        \part
        Give an example of 2 matrices $A$ and $B$ such that $A$ and $B$ each have
        nullity 1 but $AB$ has nullity 0.
        \part
        Give an example of 2 matrices $A$ and $B$ such that $A$ and $B$ each have
        nullity 0 but $AB$ has nullity 1.
        \part
        Give an example of a diagonalizable matrix that is not invertible.
        \part
        Give an example of an invertible matrix that is not diagonalizable.
        \part
        Give an example of a symmetric matrix that is not diagonalizable.
        \part
        Give an example of a symmetric matrix that is not invertible.
        \part
        Give an example of an orthogonal matrix that is not invertible.
        \part
        Give an example of an invertible matrix that is not orthogonal.
        \part
        Give an example of a matrix with distinct eigenvalues that is not
        invertible.
        \part
        Give an example of a $3\times 3$ orthogonal matrix with only one eigenvalue.
        \part
        Give an example of a $3\times 3$ matrix whose only eigenvalue is 2.
        \part
        Give an example of a $3\times 3$ invertible matrix whose only
        eigenvalue is 2.
        \part
        Give an example of a matrix $A$ and an eigenvalue $\lambda$ such that
        the algebraic multiplicity of $\lambda$ is less than the geometric
        multiplicity.
        \part
        Give an example of a matrix $A$ and an eigenvalue $\lambda$ such that
        the geometric multiplicity of $\lambda$ is less than the algebraic
        multiplicity.
        \part
        Give an example of a matrix $A$ and an eigenvalue $\lambda$ such that
        the eigenspace is 0-dimensional.
   \end{parts}
\end{questions}

\end{document}
