\documentclass{article}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{parskip}
\begin{document}

\textbf{\huge  Math 126F - Summer 2017 }
\begin{itemize}
    \item
        Instructor: Kevin Lui
    \item
        Email: \href{mailto:klui@uw.edu}{klui@uw.edu}
    \item
        Webpage: \url{https://sites.math.washington.edu/~klui/}
    \item
        Office: Padelford C-8D
\end{itemize}

\textbf{Office Hours}
Office hours are held in Padelford C-8D.
\begin{itemize}
    \item
        Monday: 9:30 -- 10:30
    \item
        Wednesday: 2:30 -- 3:30
\end{itemize}

\textbf{WebAssign/Book}

We will use \textit{Multivariable Calculus 7th Edition} by James Stewart. You must
have a WebAssign code to complete the homework. This code gives access to a
electronic version of the book. Dr. Andrew Loveless wrote some really detailed
instructions on WebAssign here:
\url{https://sites.math.washington.edu/~m124/WebassignInstructions.pdf}

\textbf{Objectives}

We will cover most of Chapter 10, 12, 13, 14, 15 in Stewart and the UW Taylor
Series Notes. You will learn vectors and vector functions, multivariable
functions, partial derivatives, tangent places, higher dimensional integrals,
taylor series and taylor approximations.

\textbf{Grading}

The class is curved in such a way that the median score will be around a 2.9. I
will provide a grade estimate after each midterm.  The grades will be weighed
as follows:

\begin{tabular}{ l r }
    Category  & Weight   \\
    \hline
    Homework  & 10\%      \\
    Quizzes   & 10\%      \\
    Midterm 1 (7/13) & 25\%      \\
    Midterm 2 (8/3) & 25\%      \\
    Final (8/18)    & 30\%
\end{tabular}

\textbf{Homework}

Homework assignments are done through WebAssign. The due dates for each
assignment will be posted there. You are expected to complete each assignment 2
days before the official due date. I will not grant homework extensions.

I will add 5\% to your homework grade unless you are already above a 95\%.

\textbf{Quiz Sections}

You are expected to attend quiz sections. In general, quiz sections are an
opportunity for you to review course material with the TA. There will be
quizzes. They are on 6/29, 7/6, 7/20, 7/27, 8/10.

\textbf{Exams}

The midterms are held in quiz sections and the final is held in lecture. You
are allowed the Ti-30x IIS calculator and a single sheet of 2-sided handwritten
self written notes.

\textbf{Makeup Quizzes and Exams}

There will be no makeup quiz or exams. You are excused from quizzes and exams
in special circumstances.

In the case of religious holidays or participation in certain university
sponsored events, arrangements must be made as soon as possible. Otherwise, I
will excuse you from a quiz or exam only in unavoidable, compelling, and
well-documented circumstances. If you are extremely sick, you must bring me a
doctor's note that states you were incapable of taking the quiz or exam. If you
are excused from a midterm, your other midterm and final will be weighed more
heavily. If you are excused from a quiz, your other quizzes will be weighed
more heavily.

If you are not excused and you miss a quiz or exam, you will receive a zero.


Much of this syllabus was taken from Dr. Andrew Loveless.
\end{document}
