\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}

\textbf{\huge  Math 308I - Spring 2019}
\begin{itemize}
    \item
        Instructor: Kevin Lui
    \item
        Email: \href{mailto:klui@uw.edu}{klui@uw.edu}
    \item
        Webpage: \url{kevinlui.org}
    \item
        Office: Padelford C-8D
\end{itemize}

\textbf{Office Hours}
See the course page for office hours.

\textbf{WebAssign/Book}

We will use \textit{Linear Algebra with Applications, Second Edition} by
Jeffrey Holt. You need a WebAssign access code to complete the homework. You
can obtain this through the bookstore.

\textbf{Objectives}

The goal of this course is to introduce students to matrix algebra. Topics
include linear systems of equations, linear independence and span, linear
transformations, inverses, vector spaces, determinants, eigenvalues and
eigenvectors.

\textbf{Grading}

The class is curved in such a way that the median score will be around a 2.9 or
3.0. The grades will be weighed as follows:

\begin{tabular}{ l r }
    Category  & Weight   \\
    \hline
    Homework  & 20\%      \\
    Midterm 1 (Week 4 - 4/26) & 20\%      \\
    Midterm 2 (Week 8 - 5/24) & 20\%      \\
    Final (Final Week - Jun 10)    & 40\%
\end{tabular}

\textbf{Homework}

The homework is done through Webassign. The due dates for the Webassign
homework will be posted on the Webassign page. I will add 5\% to your
Webassign grade unless you are above a 95\%. In that case, you will receive a
100\%.

\textbf{Exams}

You are allowed the Ti-30x IIS calculator and a single sheet of 2-sided
handwritten self written notes.

\textbf{Makeup Exams}

There will be no makeup midterm.

In the case of religious holidays or participation in certain university
sponsored events, arrangements must be made as soon as possible. Otherwise, I
will excuse you from an exam only in unavoidable, compelling, and
well-documented circumstances. If you are extremely sick, you must bring me a
doctor's note that states you were incapable of taking the quiz or exam. If you
are excused from a midterm, your other midterm and final will be weighed more
heavily. If you are excused from final, you will receive an incomplete and will
take a makeup final the following quarter.

If you are not excused and you miss an exam, you will receive a zero.

\end{document}
